Syntax and Semantics of Abstract Binding Trees

### 2015-11-08 paper.tex

\title{Syntax and Semantics of Indexed Abstract Binding Trees}
\date{}
\author{Jon Sterling and Darin Morrison}
\maketitle

@@

In \emph{Practical Foundations for Programming Languages} \cite{harper:2016},
Robert Harper develops the multi-sorted version of abstract binding trees and
proposes an extension to include families of operators indexed by
\emph{symbols}, which are, unlike variables, subject to only
distinctness-preserving renaming and not substitution; furthermore, symbols do
not appear in the syntax of abts, and are only introduced as parameters to
operators. This generalization to \emph{indexed abts} is essential for a
correct treatment of programming languages with open sums (e.g. ML's
\texttt{exn} type), as well as assignable references.

@@

The contribution of this paper is the development of the syntax and semantics
of \emph{indexed multi-sorted abts}, an extension of second order universal
algebra to support symbol-indexed families of operators. Additionally, we have
developed the categorical semantics for indexed abts formally in Constructive
Type Theory using the Agda proof assistant \cite{norell:2007}.

>>>>

\title{Syntax and Semantics of Abstract Binding Trees}
\date{}
\author{Jon Sterling and Darin Morrison}
\maketitle

@@

In \emph{Practical Foundations for Programming Languages} \cite{harper:2016},
Robert Harper develops the multi-sorted version of abstract binding trees and
proposes an extension to include families of operators indexed by
\emph{symbols}, which are, unlike variables, subject to only
distinctness-preserving renaming and not substitution; furthermore, symbols do
not appear in the syntax of abts, and are only introduced as parameters to
operators. This extension to support symbols is essential for a
correct treatment of programming languages with open sums (e.g. ML's
\texttt{exn} type), as well as assignable references.

@@

The contribution of this paper is the development of the syntax and semantics
of multi-sorted abts, an extension of second order universal
algebra to support symbol-indexed families of operators. Additionally, we have
developed the categorical semantics for abts formally in Constructive
Type Theory using the Agda proof assistant \cite{norell:2007}.
